Platforms for security update research

### 2014-02-06 platforms.tex
platforms: add section on hypervisors

\section{Hypervisors}
\subsection{Xen}
\subsection{VMWare}

>>>>

\section{Hypervisors}
Hypervisors try to improve security by offering a much smaller API to the VM's operating system and enforcing privilege separation by using different CPU ring levels.
Unfortunately they still have vulnerabilities which break this confinement.

\subsection{Xen}
Xen is an opensource hypervisor with a commercial version produced by Citrix.
It is widely used by lots of companies including Amazon which allow multiple mutually untrusting VMs to run on the same machine.
There is are list of vulnerabilities in Xen.\footnote{\url{http://wiki.xenproject.org/wiki/Security_Announcements_(Historical)} \url{http://xenbits.xen.org/xsa/}}
Where do we get version distribution information from?

\subsection{VMWare}
VMWare is a closed source hypervisor.
There is a list of security advisories affecting VMWare\footnote{\url{http://www.vmware.com/uk/security/advisories/}} though it also includes some other products.
Where do we get version distribution information from?
